Data analysis for employee cluster descriptive statistics

### 2023-08-10 04. Analysis/scripts/03-03-data-analysis-employee-cluster-descriptive-statistics.Rmd
Update 03-03-data-analysis-employee-cluster-descriptive-statistics.Rmd
Adding more detail to the descriptions

---
title: "Data analysis for employee cluster descriptive statistics"
date: "`r Sys.Date()`"
output: 
  html_document:
    theme: united
    highlight: tango
    code_folding: hide
params:
  author: "Ben Jaques-Leslie"
  project_number: 2312
  project_name: "Occupancy Patterns"
  google_drive_home: "G:/Shared drives/MSG Projects/1.0 Real Estate Solutions (LQ1)/2312 Work Patterns"
  data_folder_1: "prepared-data"
  data_file_1: "clusters-employee-2023-08-07.rdata"
  data_file_2: "prep_employees_2023-06-13.rdata"
  in_number_of_clusters_1: 2
  in_number_of_clusters_2: 5
  in_specification: "scale_observation_none_1_20_TRUE"

@@

```{r}
d %>% 
  group_by(.cluster_2) %>% 
  skim(exit_employment,
       multiple_supervisors,
       gsa_sso) %>% 
  as.data.frame()
```

>>>>

---
title: "Data analysis for employee cluster descriptive statistics"
date: "`r Sys.Date()`"
output: 
  html_document:
    theme: united
    highlight: tango
    code_folding: hide
params:
  author: "Ben Jaques-Leslie"
  project_number: 2312
  project_name: "Occupancy Patterns"
  google_drive_home: "G:/Shared drives/MSG Projects/1.0 Real Estate Solutions (LQ1)/2312 Work Patterns"
  data_folder_1: "prepared-data"
  data_file_1: "clusters-employee-2023-08-09.rdata"
  data_file_2: "prep_employees_2023-08-09.rdata"
  in_number_of_clusters_1: 2
  in_number_of_clusters_2: 5
  in_specification: "scale_observation_none_1_20_TRUE"

@@

```{r}
d %>% names()
```

```{r}
d %>%
  group_by(.cluster_2) %>%
  skim(exit_employment,multiple_supervisors)
```

```{r}
d %>%
  group_by(.cluster_5) %>%
  skim(exit_employment,multiple_supervisors)
```

```{r}
d %>% 
  group_by(.cluster_2) %>% 
  count(sso) %>% 
  ungroup() %>% 
  left_join(
    d %>% 
  count(.cluster_2, name = "tot")
  ) %>% 
  mutate(
    prop = n/tot
  ) %>% 
  ggplot(aes(x = sso, y =  prop,fill = .cluster_2)) +
  geom_col(position = "dodge") 
```

```{r}
d %>% 
  group_by(.cluster_5) %>% 
  count(sso) %>% 
  ungroup() %>% 
  left_join(
    d %>% 
  count(.cluster_5, name = "tot")
  ) %>% 
  mutate(
    prop = n/tot
  ) %>% 
  ggplot(aes(x = sso, y =  prop,fill = .cluster_5)) +
  geom_col(position = "dodge") +
  facet_wrap(facets = vars(sso), scales = "free")
```

Few people exit employment (~3%) and some have multiple supervisors (~26%).

Disproportionately from FAS, GSA IT, OCFO, OGP, and OHRM, and fewer in PBS

Some people exit employment (~15%) and some have multiple supervisors (~22%).

Majority are from PBS.

Almost no one (<.1%) exit employment. Some have multiple employers (20-30%).

Very few people exit employment (~3%). Some have multiple employers (20-30%).

Very few people exit employment (~2%). Some have multiple employers (20-30%).

Employees that report to the job site for most days (~97). Some days (~22) telework. Many days co-located with at least one team member (~74), supervisor (~60), or whole team (~17), but high variance. Few days (~4) where the whole team is remote, but high variance. Many working days (~119). Team is smaller (~5).

Very few people exit employment (~2%). Some have multiple employers (20-30%).

Clusters 5(5): **Non-workers**

Low number of days (~5) reporting to the site, but high variance. Some days (~27) telework, but high variance. Few days co-located with at least one team member (2)  or with supervisor (~1). Almost no days (<1) with the whole team co-located. Several days (~9) where the entire team works remotely. Few working days (~34) and high variance. Team is large (~9) and high variance.

Many people exit employment (~54%). Some have multiple employers (20-30%).
